Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-27 robdml.tex
tex

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\usepackage{enumitem}
\usepackage{multirow}
\newcommand{\uline}[1]{\underline{#1}}
\usepackage{slashbox}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{comment}

@@

Due to the flexibility of HM, any of the existing (and future) triplet samplers
can be used for calculating $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
But not all possible combinations are expected to be effective or efficient in
terms of adversarial training, as the \emph{source} hardness of a notable
portion of the given triplets should be increased.
%
Thus, we first sort the existing samplers, namely Random,
Semihard~\cite{facenet}, Softhard~\cite{revisiting},
Distance-weighted~\cite{distance}, and the within-batch Hardest negative
sampler, based on the approximated mean hardness of their outputs, as shown
in~\cref{tab:hsort}.
%
Then we adversarially train models on the CUB dataset with all combinations
respectively, and summarize the R@1 and ERS performance in \cref{tab:desth}.

@@

Recall that triplet-based model is already prone to collapse with very hard
examples, even if they are unperturbed.
%
Similarly, the model is expected to collapse with excessively hard adversarial
examples as well.
%
As shown in the last three columns of \cref{tab:desth}, almost all combinations
will result in model collapse as long as the destination hardness is softhard,
distance, or hardest.
%
The only exception is the combination of distance and hardest.
%
We empirically observe that the $E[H]$ of distance and hardest sampling are
very close to each other, which means the attack will be rather weak.
%
The model does not collapse in this case, but the robustness gain is negligible
as well.

@@

\subsection{Effectiveness of Hardness Manipulation}
\label{sec:42}

@@

@@

\subsection{Effectiveness of GA and ICS}
\label{sec:43}

@@

\subsection{Comparison with State-of-the-art}

>>>>

\usepackage{microtype}
\usepackage{xcolor}
\newcommand{\oo}[1]{\textcolor{orange}{#1}}
\include{math_commands.tex}
\usepackage{pifont}
\newcommand{\cmark}{\ding{51}}
\newcommand{\xmark}{\ding{55}}
\usepackage{enumitem}
\usepackage{multirow}
\newcommand{\uline}[1]{\underline{#1}}
\usepackage{slashbox}
\usepackage{booktabs}
\usepackage{colortbl}
\usepackage{soul}
\usepackage{comment}
\usepackage{todonotes}

@@

Due to the flexibility of HM, any of the existing (and future) triplet samplers
can be used for calculating $H_\mathsf{S}$ and $H_\mathsf{D}$.
%
But not all possible combinations are expected to be effective or efficient in
terms of adversarial training, as the \emph{source} hardness of a notable
portion of the given triplets should be increased.
%
Thus, we first sort the existing samplers, namely Random,
Semihard~\cite{facenet}, Softhard~\cite{revisiting},
Distance-weighted~\cite{distance} (\emph{abbr}., Distance), and the
within-batch Hardest negative sampler, based on the approximated mean hardness
of their outputs, as shown in~\cref{tab:hsort}.
%
Then we adversarially train models on CUB dataset with all combinations
respectively, and summarize the R@1 and ERS in \cref{tab:desth}.

@@

As shown in the last three columns of \cref{tab:desth}, almost all combinations
lead to model collapse as long as $H_\mathsf{D}$ is calculated from a Softhard,
Distance, or Hardest triplet.
%
Due to the small $E[H_\mathsf{D}-H_\mathsf{S}]$ in the combination of Distance
and Hardest triplets, the adversarial examples will be weak and the model does
collapse, but the robustness gain is negligible.

\todo{Rev}

@@

\subsection{Effectiveness of Our Approach}
\label{sec:42}

@@

\noindent\textbf{I. Effectivenss of Hardness Manipulation}.

@@

\noindent\textbf{II. Effectiveness of Gradual Adversary}.

@@

\noindent\textbf{III. Effectivenss of Intra-Class Structure}.

\subsection{Comparison with State-of-the-art}
\label{sec:43}
